---
title: "Final Project Data Product"
author: "Marco Guado"
date: "September 15, 2016"
output: "slidy_presentation"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Resumen

The Shiny application to be developed is based on the final project (1) presented in machine learning course.
This project is to implement a model to predict what the best routine to perform an exercise with weights.
<br/>  
<br/>  
<br/>
<br/>
<br/>
<br/>
<br/>
(1) url Project used machine learning
[final] (<http://htmlpreview.github.io/?https://github.com/magzupao/machine_learning/blob/master/project_machine_learning_magz.html>)  
  
  

## Modelo

Our initial model consists of 5 measurements recorded by sensors placed; wrist, forearm and arm several people. Where A is better and E is the worst routine.<br/>

Classification:<br/>
A<br/>
B<br/>
C<br/>
D<br/>
E<br/>

It was recorded for each user samples were grouped in a matrix composed of data of 160 variables and 19622 records.             



## Process

```{r cars, include=FALSE}
url_data_training <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv";
url_data_testing <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv";

df_training <- read.csv(url(url_data_training));
df_testing <- read.csv(url(url_data_testing));

tmp_df_training <- df_training[, c(8:160)];
tmp_df_testing <- df_testing[, c(8:160)];

#Clean data
not.na <- function(){
    pos_columns <- c()
    for(column in c(1:153)){
        exist.na <- sum(is.na(tmp_df_testing[,column]))
        if(20 == exist.na ){
            #print("exist")
        }else{
            #print("not exist")
            pos_columns <- c(pos_columns, column)
        }       
    }
    return(pos_columns)
}

columns <- not.na();

#We create two new data set that will be used for analysis
new_df_training <- tmp_df_training[, columns];
new_df_testing <- tmp_df_testing[, columns];

library(randomForest);

df_model<-randomForest(classe ~ ., data=new_df_training, ntree=30, mtry=6, replace=T);


```

After processing (data cleaning) the model, we have a data matrix consisting of 53 variables and records 19622. where we have:<br/>
<br/>
52 -> variables predictors<br/>
1  -> variable discriminant<br/>
<br/>
<br/>
Based on the analysis model where we have quantitative and qualitative variables can solve a case prediction algorithm using the Random Forest.


## Results

Our model with a value of tree = 30 ---> 100 is stable, and has a very low tracking error, which is reliable.

```{r df_model}
plot(df_model)
```


